VOI-aware Monte-Carlo Sampling in Trees

### 2011-12-18 paper/vago/paper.tex
softer formulation of relation to hay and russell

In order to estimate the VOI of pulling an arm, a sampling model is needed.
The generic sampling model used is: the actual value of an arm has a certain distribution.
Pulling an arm is an i.i.d. noisy measurement of the actual value of the arm.
In \cite{HayRussell.MCTS}, Section 4, two instances of this model are
examined:
\begin{enumerate}[a)]
\item uniformly distributed prior of the value, with Bernouli
  sampling, and 
\item normally distributed prior of the value, with normally
  distributed sampling.
\end{enumerate}

Here we examine the same general setting (i.i.d. samples), but instead
of using a specific distribution model, use {\em concentration
  inequalities} to derive distribution-independent bounds on the
VOI. Our bounds are applicable to any distribution that conforms to
our assumptions, including the case of normally distributed prior of
the value, with normally distributed sampling.

>>>>

In order to estimate the VOI of pulling an arm, a sampling model is
needed.  The generic sampling model used is: 
\begin{itemize}
\item The actual value of an arm has a certain distribution.
\item Pulling an arm is an i.i.d. noisy measurement of the actual
  value of the arm.
\end{itemize}
In \cite{HayRussell.MCTS}, Section 4, two instances of this model are
examined:
\begin{enumerate}[a)]
\item uniformly distributed prior of the value, with Bernouli
  sampling, and 
\item normally distributed prior of the value, with normally
  distributed sampling.
\end{enumerate}
Here we examine the same general setting (i.i.d. samples), but instead
of using a specific distribution model, use {\em concentration
inequalities} to derive distribution-independent bounds on the
VOI. Our bounds are applicable to any bounded distribution. Similar
bounds can be derived for certain unbounded distributions, such as the
normally distributed prior of the value with normally disributed
sampling, a subject of future work.
